Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
presented -> present
revise normal coercion

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -Jeremy}

\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -Jeremy}

\todo[inline]{BTW, using the Coercion and Blame paper as a model for
  how to write papers is perhaps not the best idea. That paper intentionally
  diverged from the normal paper format in several ways. You can
  do that too after you've become a master at writing papers.
  For now you are much better off following the advice of
  Simon Peyton Jones about how to write a paper (google it).}

@@

\citet{siek2012interpretations} present a revised coercion calculi.
\todo[inline]{Actually, Wadler might disagree that the blame calculus is
  a lazy UD calculus... because the blame calculus has polarity in the blame
  labels, and the lazy UD calculus does not. So perhaps we should just
  say lazy UD cast calculus, and explain that it is very close to the
  blame calculus. -Jeremy}
\todo[inline]{I replace most uses of blame calculus to cast calculus. -KC}
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} Blame 
	Calculus}
	\label{machine-cekc}
\end{figure}

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy}
\todo[inline]{The definition of values is too loose for a cast.
  You need to restrict the casts to just the inert ones. -Jeremy }
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

\todoKC{change the reduction rules of case}

@@

In this section we review the normal coercions (NC) of 
\citet{siek2012interpretations}.
\todo[inline]{Don't abbreviate to NC. -Jeremy}
We ignore sum types and product types in this 
section, because they were not presented in the paper. We assume a basic 
familiarity with coercion, and direct readers who do not know it to 
\citet{siek2012interpretations}.

As the name suggests, 
hypercoercion is largely inspired by coercion, especially its subst NC.
\todo[inline]{``subst'' is not a word.}
We 
will highlight the similarity of normal coercion and hypercoercion, and hope 
this would convince you that hypercoercion should be as difficult to implement 
as NC.

\todo[inline]{I don't think we should try to convince the reader that
  hypercoercions are easier to implement. We don't have real evidence
  for that.}

@@

\figref{fig:normal-coercion} defines the normal coercion.
\todo[inline]{Give a summary statement about the shape of the normal form.}
Types, pre-types, and blame labels are as before.
Let $ I $ range over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ range over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ range over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
re-arrange cases a little bit, the definition becomes:
\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

Three observations on this definition leads to hypercoercion: 
\begin{enumerate}
	\item The length of normal coercion is at most three.
	\item Projections are always at the beginning when presented.
          \todo[inline]{change ``presented'' to ``present''. }
	\item Injections and failures are always at the end when presented.
          \todo[inline]{change ``presented'' to ``present''. }
\end{enumerate}

>>>>

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -Jeremy}
\todo[inline]{Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -Jeremy}

@@

\citet{siek2012interpretations} present a revised coercion calculi.
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

	\caption{CEK abstract machine ($ \mathcal{D} $) for the \lazyD{} cast 
	calculus}
	\label{machine-cekc}
\end{figure}

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines \citep{felleisen1986control}.
\todo[inline]{Briefly present the main ideas regarding how a CEK
  machine works. (2-3 sentences) -Jeremy}
\todo[inline]{Use citep to put a citation in parentheses, as I've
  done above. -Jeremy }
\todo[inline]{The figure is too tall. You may need to pull some things
  out of the figure, such as the value typing. -Jeremy}
\todo[inline]{Please fill in the missing reduction rules. -Jeremy}
\todo[inline]{Explain why you are using a CEK machine instead of
  reduction semantics. -Jeremy}
\todo[inline]{Change the order of parameters for applyCast to take
  the value first and the cast second. -Jeremy}
We conjecture that this CEK machines agree with the \lazyD{} cast calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hypercoercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hypercoercions.

@@

In this section we review the normal coercions \citep{siek2012interpretations} 
to motivate the design of hypercoercion. 
We ignore sum types and product types in this 
section, because they were not in the paper. We assume a basic 
familiarity with coercion, and direct readers who do not know it to 
\citet{siek2012interpretations}.
%We 
%will highlight the similarity of normal coercion and hypercoercion, and hope 
%this would convince you that hypercoercion should be as difficult to implement 
%as normal coercions.
%\todo[inline]{I don't think we should try to convince the reader that
%  hypercoercions are easier to implement. We don't have real evidence
%  for that.}

@@

\todo[inline]{Give a summary statement about the shape of the normal form.}
\todo[inline]{The three-part shape is not obvious before the transformation at 
the end of the next paragraph. So the summary is given after that. -KC}

\figref{fig:normal-coercion} defines the normal coercion.
Types, pre-types, and blame labels are as before.
Let $ I $ range over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ range over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ range over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
re-order the cases, the definition of $ \hat{c} $ becomes:
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

Three observations on this definition leads to hypercoercion: 
\begin{enumerate}
	\item The length of normal coercion is at most three.
	\item Projections are always at the beginning when present.
	\item Injections and failures are always at the end when present.
\end{enumerate}
